Diversity dynamics in Nymphalidae butterflies: Effect of phylogenetic uncertainty on diversification rate shift estimates

### 2014-11-12 MS_revised.tex
in only a few
ready for resubmittion
one ref was missing

\documentclass[10pt]{article}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{cite}
\usepackage{hyperref}
\usepackage{microtype}
\usepackage{lineno}
\linenumbers
\DisableLigatures[f]{encoding = *, family = * }

@@

The results from BAMM recovered only two significant shifts in our MCC tree
as this method seems to be much more conservative than the MEDUSA approach.
One of these 
shifts is the Satyrini clade. MEDUSA estimated its parent node as
significant shift in a few trees from the posterior distribution. 
Thus, it might be important to
take into account phylogenetic uncertainty in BAMM as well.

@@

\section*{Supporting Information Legends}
\begin{description}
 \item {\bf Supporting Information S01.nex.} MCC Nymphalidae tree from
{[}13{]}

>>>>

\documentclass[10pt]{article}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{cite}
\usepackage{hyperref}
\usepackage{lineno}
\usepackage{microtype}
\DisableLigatures[f]{encoding = *, family = * }

@@

The results from BAMM recovered only two significant shifts in our MCC tree
as this method seems to be much more conservative than the MEDUSA approach.
One of these 
shifts is the Satyrini clade. MEDUSA estimated its parent node as
significant shift in only a few trees from the posterior distribution. 
Thus, it might be important to
take into account phylogenetic uncertainty in BAMM as well.

@@

\section*{Supporting Information Legends}
\begin{description}
 \item {\bf Supporting Information S01.nex.} MCC Nymphalidae tree from
\cite{wahlberg2009}
